Detecting strongly lensed quasars by pixel-level model comparison

### 2014-05-15 docs/paper1.tex
Paragraph on wide field imaging

>>>>

Wide field optical imaging survey data have, generically, the  property
that the image quality varies from epoch to epoch, and so between images
taken in different filters. This results from the need to cover large areas
of sky at low overhead. An advantage of this observing strategy is that the
multiplicity of images allows missing data or poor image quality in any
given single exposure to be corrected for by the other exposures. To
capitalise on this, and to extract as much information as possible from the
data, we propose a joint fit of the same model to all images
simultaneously. We do this using the flexible image fitting software ``The
Tractor'' (Lang \& Hogg 2014). This approach is optimal in terms of its
potential for information extraction, but its cost is to be investigated.
